{\small Filamentary transport in high-power H-mode conditions and in no/small-ELM regimes to predict heat and particle loads on PFCs for future devices}

### 2017-11-13 Meetings/GPMNov2017/gpm_november2017_topic21.tex
Update to GPM slides

\begin{frame}{2017 Top Objectives 
    12.12.2016}
  \Fontvi
\vspace{-1cm}
Deliverables listed during the call for manning of last December 
\begin{enumerate}
\item \only<2>{\color{ta3chameleon}} Provide cross-machine L-Mode
  shoulder dependence on current both at constant B$_t$ and at
  constant $q_{95}$
\item \only<2>{\color{orange}}Establish robust scenario for density
  shoulder profile in H-Mode and establish dependence on
  fuelling/neutral profiles/divertor conditioon
\item \only<2>{\color{green}}Use the new HHF probe on AUG to study
  filamentary transport under high-power H-Mode conditions \only<2>{\color{red}}and under
  different plasma configurations (SN, DN)
\item \only<2>{\color{orange}}Study the role of ELM regimes,  neutral
  compression and particle density in filamentary transport and
  related shoulder formation
\item \only<2>{\color{orange}} Identify the contribution of
  collisionality and seeding on filamentary transport and related
  shoulder formation
\item \only<2>{\color{red}}Determine the effect of filaments and
  shoulder formation on target heat loads in different H-mode plasmas
\end{enumerate}
\onslide<2>{
  So far H-Mode operation has been limited to AUG since no operational
  scenarion in high-density NBH heated plasma on TCV has been established
}
\end{frame}

@@

\begin{frame}{Matching scenarios with cryo-pumps}
\Fontvi
  \vspace{-1cm}
\begin{columns}
  \begin{column}{0.65\textwidth}
    \centering{\includegraphics<1>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/CompareShot34276_34281}}
    \centering{\includegraphics<2>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/PuffingIpolsola34276_34281}}
    \centering{\includegraphics<3>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/EvolutionEdgeProfiles_34276_34281}}
    4\centering{\includegraphics<4>[height=0.9\textheight]{../../Experiments/AUG/analysis/pdfbox/Shot_34278_34281_InterELMprofiles}}
  \end{column}
  \begin{column}{0.35\textwidth}
    \begin{itemize}
      \item<1-> To match similar edge density and divertor pressure
        and to reach the same level of detachment we increase the
        fueling by almost a factor of 3, increasing also the rate. In
        addition to that we also increase substantially the N
        puffing. \alert{Degraded H-Mode reached earlier in density
          without the cryopumps}
      \item<2-> Similar ELMy behavior obtained during the density ramp  
      \item<3-> Now the scenario suggest a strong profile flattening
        even with the cryopumps
       \item<4> Inter-ELM resolved Li-Be profiles confirm this with
         shoulder formed with similar strength even with the cryopumps
         in operation.
    \end{itemize}
  \end{column}
\end{columns}
\end{frame}

@@

\begin{frame}{Program for 2018: AUG}
  \begin{itemize}
     \item X-point manipulator (hopefully with NPH) triggered at
	the same time as MPM
     \item X-point vertical shift in order to have SP at different
	vertical heigth at the target
     \item DN discharges. With slow movement of the second X-point into the vessel
	to be performed at constant power/density where shoulder alreay exists
     \item USN with midplane/X-point manipulator to monitor the upstream SOL  \end{itemize}
\end{frame}

>>>>

\begin{frame}{2017 Top Objectives 
    12.12.2016}
  \Fontvi
\vspace{-1cm}
Deliverables listed during the call for manning of last December 
\begin{enumerate}
\item \only<2>{\color{ta3chameleon}} Provide cross-machine L-Mode
  shoulder dependence on current both at constant B$_t$ and at
  constant $q_{95}$
\item \only<2>{\color{taorange}}Establish robust scenario for density
  shoulder profile in H-Mode and establish dependence on
  fuelling/neutral profiles/divertor conditioon
\item \only<2>{\color{ta3chameleon}}Use the new HHF probe on AUG to study
  filamentary transport under high-power H-Mode conditions \only<2>{\color{consorziored}}and under
  different plasma configurations (SN, DN)
\item \only<2>{\color{taorange}}Study the role of ELM regimes,  neutral
  compression and particle density in filamentary transport and
  related shoulder formation
\item \only<2>{\color{taorange}} Identify the contribution of
  collisionality and seeding on filamentary transport and related
  shoulder formation
\item \only<2>{\color{consorziored}}Determine the effect of filaments and
  shoulder formation on target heat loads in different H-mode plasmas
\end{enumerate}
\onslide<2>{
  So far H-Mode operation has been limited to AUG since no operational
  scenarion in high-density NBH heated plasma on TCV has been established
}
\end{frame}

@@

\begin{frame}{Matching scenarios with cryo-pumps}
\Fontvi
  \vspace{-1cm}
\begin{columns}
  \begin{column}{0.65\textwidth}
    \centering{\includegraphics<1>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/CompareShot34276_34281}}
    \centering{\includegraphics<2>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/PuffingIpolsola34276_34281}}
    \centering{\includegraphics<3>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/EvolutionEdgeProfiles_34276_34281}}
    \centering{\includegraphics<4>[height=0.9\textheight]{../../Experiments/AUG/analysis/pdfbox/Shot_34278_34281_InterELMprofiles}}
    \centering{\includegraphics<5>[height=0.9\textheight]{../../Experiments/AUG/analysis/pdfbox/CompareCas34278_34281}}
  \end{column}
  \begin{column}{0.35\textwidth}
    \begin{itemize}
      \item<1-> To match similar edge density and divertor pressure
        and to reach the same level of detachment we increase the
        fueling by almost a factor of 3, increasing also the rate. In
        addition to that we also increase substantially the N
        puffing. \alert{Degraded H-Mode reached earlier in density
          without the cryopumps}
      \item<2-> Similar ELMy behavior obtained during the density ramp  
      \item<3-> Now the scenario suggest a strong profile flattening
        even with the cryopumps
       \item<4-> Inter-ELM resolved Li-Be profiles confirm this with
         shoulder formed with similar strength even with the cryopumps
         in operation.
         \item<5> We can also confirm that additional fueling change
           substantially the blob size which increases consistently
           with the modification of $\Lambda_{div}$
    \end{itemize}
  \end{column}
\end{columns}
\end{frame}

@@

\begin{frame}{Program for 2018: AUG}
  \begin{itemize}
     \item X-point manipulator (hopefully with NPH) triggered at
	the same time as MPM
     \item X-point vertical shift in order to have SP at different
	vertical heigth at the target. \alert{This could suggest us if
        similar behavior as the one observed on JET are visible at AUG}
     \item DN discharges. With slow movement of the second X-point into the vessel
	to be performed at constant power/density where shoulder
        alreay exists. \alert{This is mandatory to complement the
          information obtained on TCV}
     \item USN with midplane/X-point manipulator to monitor the upstream SOL 
\end{itemize}
 \end{frame}
